Staged Abstract Interpreters

### 2019-09-03 paper/paper.tex
revise intro
revision
update
misc update
ack

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.83]{beramono}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{MnSymbol}
\usepackage{xcolor,colortbl}
\usepackage{url}
\usepackage{listings}
\usepackage{paralist}
%\usepackage[compact]{titlesec}
\usepackage[font={small}]{caption}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{flushend}
\usepackage{bcprules}

@@

@@

%% Title information
%\title{Staged Abstract Interpreters}         %% [Short Title] is optional;
\title{Staging Abstract Interpreters}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Fast and Compositional Whole-Program Analysis for Free}                     %% \subtitle is optional
\subtitle{Fast and Modular Whole-Program Analysis via Meta-Programming}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Author with single affiliation.
\author{Guannan Wei}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  %\position{Position1}
  \department{Department of Computer Science}              %% \department is recommended
  \institution{Purdue University}            %% \institution is required
  %\streetaddress{305 N. University Street}
  %\city{West Lafayette}
  %\state{IN}
  %\postcode{47906}
  \country{USA}                    %% \country is recommended
}
\email{guannanwei@purdue.edu}          %% \email is recommended

%% Author with two affiliations and emails.
\author{Yuxuan Chen}
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  %\position{Position2a}
  \department{Department of Computer Science}             %% \department is recommended
  \institution{Purdue University}           %% \institution is required
  %\streetaddress{305 N. University Street}
  %\city{West Lafayette}
  %\state{IN}
  %\postcode{47906}
  \country{USA}                    %% \country is recommended
}

\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  %\position{Position2b}
  %\department{Department2b}             %% \department is recommended
  \institution{Facebook}           %% \institution is required
  %\streetaddress{Street3b Address2b}
  %\city{City2b}
  %\state{State2b}
  %\postcode{Post-Code2b}
  \country{USA}                   %% \country is recommended
}
\email{first2.last2@inst2b.org}         %% \email is recommended

\author{Tiark Rompf}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  %\position{Position1}
  \department{Department of Computer Science}              %% \department is recommended
  \institution{Purdue University}            %% \institution is required
  %\streetaddress{305 N. University Street}
  %\city{West Lafayette}
  %\state{IN}
  %\postcode{47906}
  \country{USA}                    %% \country is recommended
}
\email{tiark@purdue.edu}          %% \email is recommended

@@

%% Acknowledgments
% Ack Fei, Greg, James, Qianchuan, Guanhong
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.83]{beramono}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{MnSymbol}
\usepackage{color}
\usepackage{xcolor,colortbl}
\usepackage{url}
\usepackage{listings}
\usepackage{paralist}
%\usepackage[compact]{titlesec}
\usepackage[font={small}]{caption}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{flushend}
\usepackage{bcprules}

@@

\definecolor{light-gray}{gray}{0.85}

@@

%% Title information
%\title{Staged Abstract Interpreters}         %% [Short Title] is optional;
\title{Staged Abstract Interpreters}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Fast and Compositional Whole-Program Analysis for Free}                     %% \subtitle is optional
\subtitle{Fast and Modular Whole-Program Analysis via Meta-Programming}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Author with single affiliation.
\author{Guannan Wei}
\author{Yuxuan Chen}
\author{Tiark Rompf}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  %\position{Position1}
  \department{Department of Computer Science}              %% \department is recommended
  \institution{Purdue University}            %% \institution is required
  %\streetaddress{305 N. University Street}
  %\city{West Lafayette}
  %\state{IN}
  %\postcode{47906}
  \country{USA}                    %% \country is recommended
}
\email{guannanwei@purdue.edu}          %% \email is recommended
\email{chen1797@purdue.edu}
\email{tiark@purdue.edu}          %% \email is recommended

%% Author with two affiliations and emails.
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This work was supported in part by NSF awards 1553471, 1564207, 1918483, DOE
  award DE-SC0018050, as well as gifts from Google, Facebook, and VMware.

  \iffalse
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
  \fi
\end{acks}
